---
title: "kayadata"
author: "Jonathan Gilligan"
date: "2022-04-14"
output: github_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  echo = FALSE, 
  comment = "#>",
  fig.path="man/figures/README-",
  out.width = "100%"
  )
library(tidyverse)
# library(pacman)
# p_load_current_gh("jonathan-g/kayadata")
library(kayadata)
```
# kayadata

<!-- badges: start -->
[![CRAN Status Badge](https://www.r-pkg.org/badges/version-last-release/kayadata)](https://cran.r-project.org/package=kayadata)
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.6462452.svg)](https://doi.org/10.5281/zenodo.6462452)
[![License: MIT](https://img.shields.io/badge/License-MIT-yellow.svg)](https://opensource.org/licenses/MIT)
[![R-CMD-check](https://github.com/jonathan-g/kayadata/workflows/R-CMD-check/badge.svg)](https://github.com/jonathan-g/kayadata/actions)
<!-- badges: end -->

This package loads Kaya-identity data, synthesized from several sources.

To install the package from CRAN:
```{r initialize, echo=TRUE, eval=FALSE}
install.packages("kayadata")
```
Once you've installed it, then you just need to use the command 
`library(kayadata)` to load the package.

Some of the functions the package provides are:

* `kaya_region_list()`: Get a list of available countries and regions.
* `get_kaya_data()`: Get data for a specific country. 
  Example: 
```{r get-kaya-data, echo=TRUE}
mexico_data = get_kaya_data("Mexico") 
mexico_data %>% filter(year >= 1965) %>% 
  select(region:ef) %>%
  head()
```
* `project_top_down()`: Project future population, GDP, energy use, and 
  emissions. 
  Example: 
```{r project-top-down, echo=TRUE}
mexico_2050 = project_top_down("Mexico", 2050)
mexico_2050
```
* `plot_kaya`: Plot trends in Kaya variables for a given region or country.
  Example:
```{r plot-kaya, echo=TRUE}
us_kaya = get_kaya_data("United States")
plot_kaya(us_kaya, "ef", y_lab = "Carbon intensity of economy",
          start_year = 2000, stop_year = 2010, log_scale = TRUE,
          trend_line = TRUE)
```
```{r plot-kaya-world, echo=TRUE}
world_kaya = get_kaya_data("World")
plot_kaya(world_kaya, "P", start_year = 2000, stop_year = 2010, log_scale = FALSE,
          trend_line = FALSE)
```
* `get_fuel_mix`: Get the fuel mix (coal, gas, oil, nuclear, and renewables) 
  for a region or country. 
  Example: 
```{r get-fuel-mix, echo=TRUE}
mexico_mix = get_fuel_mix("Mexico")
mexico_mix
```
* `plot_fuel_mix`: Plot the fuel mix in a donut chart
```{r plot-fuel-mix, echo=TRUE}
plot_fuel_mix(mexico_mix)
```

After you install the package, you can get more help inside RStudio by typing 
`help(package="kayadata")` in the R console window.

## Code of conduct

Please note that this project is released with a [Contributor Code of
Conduct](https://jonathan-g.github.io/kayadata/CODE_OF_CONDUCT.html). By
participating in this project you agree to abide by its terms.
