---
title: "kayadata"
author: "Jonathan Gilligan"
date: "2018-08-13"
output: 
  md_document:
    variant: markdown_github
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# library(pacman)
# p_load_current_gh("jonathan-g/kayadata")
library(kayadata)
```
# kayadata

**GitHub:** [![Build Status](https://travis-ci.org/jonathan-g/kayadata.svg?branch=master)](https://github.com/jonathan-g/kayadata/commits/master)

**GitLab:** [![Build Status](https://gitlab.jgilligan.org/gilligan_teaching/ees_3310/ees_3310_software/kayadata/badges/master/build.svg)](https://gitlab.jgilligan.org/gilligan_teaching/ees_3310/ees_3310_software/kayadata/commits/master)


This package loads Kaya-identity data, synthesized from several sources.

To install and load the package, first install either the `pacman` or `devtools` 
package from CRAN:
```{r initialize, echo=TRUE, eval=FALSE}
install.packages("devtools")
devtools::install_github("jonathan-g/kayadata")
library(kayadata)
```
or
```{r initialize-pacman, echo=TRUE, eval=FALSE}
install.packages("pacman")
library(pacman)
p_load_gh("jonathan-g/kayadata")
```

Once you've installed it, then you just need to use the command 
`library(kayadata)` to load the package.

Some of the functions the package provides are:

* `kaya_region_list()`: Get a list of available countries and regions.
* `get_kaya_data()`: Get data for a specific country. 
  Example: 
```{r get-kaya-data, echo=TRUE}
finland_data = get_kaya_data("Finland")
head(finland_data)
```
* `project_top_down()`: Project future population, GDP, energy use, and 
  emissions. 
  Example: 
```{r project-top-down, echo=TRUE}
finland_2050 = project_top_down("Finland", 2050)
finland_2050
```
* `get_fuel_mix`: Get the fuel mix (coal, gas, oil, nuclear, and renewables) 
  for a region or country. 
  Example: 
```{r get-fuel-mix, echo=TRUE}
finland_mix = get_fuel_mix("Finland")
finland_mix
```
* `plot_kaya`: Plot trends in kaya variables for a given region or country.
  Example:
```{r plot-kaya}
us_kaya = get_kaya_data("United States")
plot_kaya(us_kaya, "ef", start_year = 2000, stop_year = 2010, log_scale = TRUE,
          trend_line = TRUE)
```
```{r plot-kaya-world}
world_kaya = get_kaya_data("World")
plot_kaya(world_kaya, "P", start_year = 2000, stop_year = 2010, log_scale = FALSE,
          trend_line = FALSE)
```

After you install the package, you can get more help inside RStudio by typing 
`help(package="kayadata")` in the R console window.
